\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{// All comments are NOT created equal}

### 2014-11-28 Proposal.tex
switch to bibtex

\usepackage{titlesec} % Allows customization of titles
%\renewcommand\thesection{\Roman{section}} % Roman numerals for the sections
%\renewcommand\thesubsection{\Roman{subsection}} % Roman numerals for subsections
\titleformat{\section}[block]{\large\scshape\centering}{\thesection.}{1em}{} % Change the look of the section titles
\titleformat{\subsection}[block]{\large}{\thesubsection.}{1em}{} % Change the look of the section titles

\usepackage{fancyhdr} % Headers and footers
\pagestyle{fancy} % All pages have headers and footers
\fancyhead{} % Blank out the default header
\fancyfoot{} % Blank out the default footer
\fancyhead[C]{Naomi Pentrel $\bullet$ \href{mailto:n.pentrel@jacobs-university.de}{n.pentrel@jacobs-university.de} $\bullet$ \today} % Custom header text
\fancyfoot[RO,LE]{\thepage} % Custom footer text
\usepackage{graphicx}
\usepackage{wrapfig}

@@

The OMDoc (Open Mathematical Documents) format is a content markup scheme for mathematical documents.\cite{OMDoc book} Using OMDoc, this research aims to visualize the connections of some of what is written about Mathematics or other fields in a way that allows students to learn the concepts the current topic depends on should they require to refresh their memories. As such it will foster learning and could transform how we interact with course material as a whole. It is easy to see that this research would also have many other real world applications anywhere where knowledge is supposed to be transferred.\\

@@

The Semantic Web approach aims to transform the World Wide Web (WWW) from a mere information space to an information web that is processable by machines.\cite{SemWeb} There exists an interesting similarity in other fields such as that of new presentation tools that aim to enable you to present information in a more interconnected way that provides context. Both developments strive to connect pieces of information and through providing context elevate pure information that is provided to knowledge.\\

These two developments have more in common than one would think. Looking at the history of the WWW, the era of Web 2.0, where everyone is now able to generate content lead to a lot of information but comparatively little knowledge.\cite{Weller} Here the processing of information to provide knowledge is lacking. Similarly I would argue that the existance of tools like Powerpoint have lead to virtually everyone doing presentations. As everyone who has witnessed many presentation knows, these are easily compared to blogs: they contain some knowledge but are often badly delivered and lack structure and context.\\

@@

\ednote{INSERT GRAPH that leads from info to knowledge
\cite{Probst} \\}

"Knowledge is the information necessary to support intelligent reasoning." \cite{Kohlhase} That said, it is imperative to facilitate knowledge transfer.  Thus, we will examine how visually representing information and its context can make knowledge transfer easier. For this we will be examining the OMDoc (Open Mathematical Documents) format as the example that will provide us with an annotated set of documents of which we will visualize the dependencies of the contained information. We will however not visualize the dependencies as a simple graph but use an API such as Impress.js to allow for us to show the current piece of information of interest in context with dependent information.\\

@@

In linguistics the concept of information packaging is know. Within this, one discriminates between \textit{familiar} and \textit{old} information. Familiar information is shared by speaker and addressee whereas new information not. In addition one distinguishes information that is old or new with respect to the discourse or with respect to the addressee.\\

@@

In this example in the first part of the sentence information pertaining to my sister and to a circus are introduced, i.e. \textit{discourse-new}. In the second part the underlined parts are considered \textit{discourse-old} since they have already been introduced.\cite{Cambridge}\\

@@

\subsection{Spatial Narrative}
The development of of presentation tools like Impress.js and Prezi, "a virtual whiteboard that transforms presentations from monologues into conversations: enabling people to see, understand, and remember ideas"\cite{Prezi}, has  changed how people think about presentations. When doing a good prezi presentation one has to understand the topic one is presenting and think about how one can portray connections between content visually.\\

The concept of Spatial Narrative stems from the establishment of frameworks for "the creation of computer-assisted flexibile 'guided tours' based on the thematically and narrative linking of a set of locations within an area into a 'spatial narrative'". An example for this is the experience of a tour guide for a certain topic.\cite{Narrative}\\

@@

The first step to implementing a \sys is to understand the tool we want to represent the knowledge in later. Since Prezi at the current time does not have an API that would allow for the generation of a whole presentation without the editor, this research will employ another tool that is inspired by the idea behind Prezi. Bartek Szopka's \textbf{Impress.js} is an open-source presentation framework which is based on CSS3 transforms and transitions.\cite{Impress} \ednote{Impressionist and jimpress}\\

@@

\newpage
\section{References}
\begin{thebibliography}{} % Bibliography - this is intentionally simple in this template

\bibitem {SemWeb}
Berners-Lee, Tim. "Semantic Web Road Map." Semantic Web Roadmap. World Wide Web Consortium, Sept. 1998. Web. 23 Nov. 2014.
\bibitem {Prezi}
"Hi, We're Prezi." Prezi.com. N.p., n.d. Web. 23 Nov. 2014.
\bibitem {Cambridge}
Huddleston, Rodney, Geoffrey K. Pullum, Laurie Bauer, Betty J. Birner, and Ted Briscoe. "Chapter 16 Information Packaging." The Cambridge Grammar of the English Language. Cambridge: Cambridge UP, 2002. N. pag. Print.
\bibitem {Kohlhase}
Kohlhase, Michael. "320441 CompLog Lecture Notes." (n.d.): n. pag. 17 Nov. 2014. Web. 19 Nov. 2014.
\bibitem {OMDoc book}
Kohlhase, Michael, and Alan Bundy. OMDoc - an Open Markup Format for Mathematical Documents. Berlin: SpringerLink, 2006. Print.
\bibitem{Narrative}
M{\o}ller-Jensen, Lasse. "Mobile GIS Strategies for Disseminating Thematic Tourist Information: Examples of Spatial Narratives." Diss. University of Copenhagen, n.d. Web. 24 Nov. 2014. \href{http://ifgi.uni-muenster.de/archives/tipugg/paper/tipugg2008_Lasse.pdf}{http://ifgi.uni-muenster.de/archives/tipugg/paper/tipugg2008\_Lasse.pdf}.
\bibitem {Probst}
Probst, Gilbert, Steffen Raub, and Kai Romhardt. \newblock Wissen Managen. \newblock Wiesbaden: S.n., 1997. Print.
\bibitem {Impress}
Szopka, Bartek. "Impress.js." Impress.js. Github, 28 Dec. 2011. Web. 23 Nov. 2014.
\bibitem {Weller}
Weller, Katrin. Knowledge Representation in the Social Semantic Web. New York: De Gruyter Saur, 2010. Print.
\end{thebibliography}

@@

\end{document}

>>>>

\usepackage{titlesec} % Allows customization of titles
%\renewcommand\thesection{\Roman{section}} % Roman numerals for the sections
%\renewcommand\thesubsection{\Roman{subsection}} % Roman numerals for subsections
\titleformat{\section}[block]{\large\scshape\centering}{\thesection.}{1em}{} % Change the look of the section titles
\titleformat{\subsection}[block]{\large}{\thesubsection.}{1em}{} % Change the look of the section titles
\usepackage{cite}
\usepackage{fancyhdr} % Headers and footers
\pagestyle{fancy} % All pages have headers and footers
\fancyhead{} % Blank out the default header
\fancyfoot{} % Blank out the default footer
\fancyhead[C]{Naomi Pentrel $\bullet$ \href{mailto:n.pentrel@jacobs-university.de}{n.pentrel@jacobs-university.de} $\bullet$ \today} % Custom header text
\fancyfoot[RO,LE]{\thepage} % Custom footer text
\usepackage{graphicx}
\usepackage{wrapfig}

@@

The OMDoc (Open Mathematical Documents) format \cite{Kohlhase:OMDoc1.2} is a content markup scheme for mathematical documents. Using OMDoc, this research aims to visualize the connections of some of what is written about Mathematics or other fields in a way that allows students to learn the concepts the current topic depends on should they require to refresh their memories. As such it will foster learning and could transform how we interact with course material as a whole. It is easy to see that this research would also have many other real world applications anywhere where knowledge is supposed to be transferred.\\

@@

The Semantic Web \cite{BernersLee:tsw98} approach aims to transform the World Wide Web (WWW) from a mere information space to an information web that is processable by machines. There exists an interesting similarity in other fields such as that of new presentation tools that aim to enable you to present information in a more interconnected way that provides context. Both developments strive to connect pieces of information and through providing context elevate pure information that is provided to knowledge.\\

These two developments have more in common than one would think. Looking at the history of the WWW, the era of Web 2.0, where everyone is now able to generate content lead to a lot of information but comparatively little knowledge \cite{Weller:npentrel14}. Here the processing of information to provide knowledge is lacking. Similarly I would argue that the existance of tools like Powerpoint have lead to virtually everyone doing presentations. As everyone who has witnessed many presentation knows, these are easily compared to blogs: they contain some knowledge but are often badly delivered and lack structure and context.\\

@@

\ednote{INSERT GRAPH that leads from info to knowledge}
\cite{ProbstRaubRomhardt}

"Knowledge is the information necessary to support intelligent reasoning." \cite{Kohlhase:Complog:base} That said, it is imperative to facilitate knowledge transfer.  Thus, we will examine how visually representing information and its context can make knowledge transfer easier. For this we will be examining the OMDoc (Open Mathematical Documents) format as the example that will provide us with an annotated set of documents of which we will visualize the dependencies of the contained information. We will however not visualize the dependencies as a simple graph but use an API such as Impress.js to allow for us to show the current piece of information of interest in context with dependent information.\\

@@

In linguistics the concept of information packaging \cite{CambridgeGrammar:npentrel14} is know. Within this, one discriminates between \textit{familiar} and \textit{old} information. Familiar information is shared by speaker and addressee whereas new information not. In addition one distinguishes information that is old or new with respect to the discourse or with respect to the addressee.\\

@@

In this example in the first part of the sentence information pertaining to my sister and to a circus are introduced, i.e. \textit{discourse-new}. In the second part the underlined parts are considered \textit{discourse-old} since they have already been introduced.\\

@@

\subsection{Spatial Narrative}
The development of of presentation tools like Impress.js and Prezi, "a virtual whiteboard that transforms presentations from monologues into conversations: enabling people to see, understand, and remember ideas" \cite{Prezi:npentrel14}, has  changed how people think about presentations. When doing a good prezi presentation one has to understand the topic one is presenting and think about how one can portray connections between content visually.\\

The concept of Spatial Narrative \cite{SpatialNarratives:npentrel14} stems from the establishment of frameworks for "the creation of computer-assisted flexibile 'guided tours' based on the thematically and narrative linking of a set of locations within an area into a 'spatial narrative'". An example for this is the experience of a tour guide for a certain topic.\\

@@

The first step to implementing a \sys is to understand the tool we want to represent the knowledge in later. Since Prezi at the current time does not have an API that would allow for the generation of a whole presentation without the editor, this research will employ another tool that is inspired by the idea behind Prezi. Bartek Szopka's \textbf{Impress.js} \cite{JSImpress:npentrel14} is an open-source presentation framework which is based on CSS3 transforms and transitions. \ednote{Impressionist and jimpress}\\

@@

\section{References}

@@

\bibliography{kwarc}{}
\bibliographystyle{alpha}
\end{document}
